What's in a Domain?: Feature Engineering for URLs

### 2022-09-16 paper/paper.tex
Paper

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain?}

@@

\begin{abstract}
Many data science problems require processing log data derived from web pages, apis or other
internet based services. URLs are one of the key pieces of information that describe almost
all types of internet activity, and hence need to be processed in a wide variety of machine 
learning applications for internet data. While URLs are structurally rich, they are not subject
to universal principles of construction making fetaure engineering for internet data challenging.

In this research we outline the key classes of approaches to deriving features from URLs and domains,
and demonstrate their utility in an open source URL fetaure engineering package url2features.
We begin with a breakdown of the broad categories of URL derived features and then discuss some of
the key implementation details, and types of problems for which they are appropriate.
\end{abstract}

>>>>

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2022}{Austin, TX}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

@@

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain?: Feature Engineering for URLs}

@@

\begin{abstract}
Many data science problems require processing log data derived from web pages, apis or other
internet traffice sources. URLs are one of the few universal pieces of information that describe
internet activity, hence URLs require effective processing for a wide variety of machine 
learning applications. While URLs are structurally rich, they are not subject
to universal principles of construction making fetaure engineering for internet data an ongoing challenge.

In this research we outline the key categories of information structure in domains and URLs.
We share an open source implementation of these ideas and demonstrate their utility across a range of 
internet traffic machine learning problems.
\end{abstract}
